### 2021-10-01 RFCs/HDF5/VOL/connector_author_guide/new_api_calls.tex

\section{New VOL API Routines}
\label{sec:api}
New API routines have been added to the HDF5 library to manage VOL connectors. This section details each new API call and explains its intended usage. Additionally, a set of API calls that map directly to the VOL callbacks themselves have been added to aid in the development of passthrough connectors which can be stacked and/or split. A list of these API calls is given in an appendix.

@@

@@

@@

\subsubsection{H5VLpeek\_connector\_by\_name}
\begin{mdframed}[style=bgbox]
\textbf{Signature:}
\begin{lstlisting}
  hid_t H5VLpeek_connector_id_by_name(const char *name); 
\end{lstlisting}
\textbf{Arguments:}\\
\begin{tabular}{l p{13.5cm}}
 {\tt name} & (IN): name of the connector to query.\\
\end{tabular}
\end{mdframed}
Retrieves the ID for a registered VOL connector based on a connector name.
This is done without duplicating
the ID and transferring ownership to the caller (as it normally the case in the
HDF5 library). The ID returned from this operation should not be closed.
This is intended for use by VOL connectors to find their own ID.
Returns a negative value ({\tt H5I\_INVALID\_HID}) on errors.
\bigskip

\subsubsection{H5VLpeek\_connector\_by\_value}
\begin{mdframed}[style=bgbox]
\textbf{Signature:}
\begin{lstlisting}
  hid_t H5VLpeek_connector_id_by_value(H5VL_class_value_t value); 
\end{lstlisting}
\textbf{Arguments:}\\
\begin{tabular}{l p{13.5cm}}
 {\tt value} & (IN): value of the connector to query.\\
\end{tabular}
\end{mdframed}
Retrieves the ID for a registered VOL connector based on a connector value.
This is done without duplicating
the ID and transferring ownership to the caller (as it normally the case in the
HDF5 library). The ID returned from this operation should not be closed.
This is intended for use by VOL connectors to find their own ID.
Returns a negative value ({\tt H5I\_INVALID\_HID}) on errors.
\bigskip

@@

@@

\subsubsection{H5VLreset\_lib\_state}
\begin{mdframed}[style=bgbox]
\textbf{Signature:}
\begin{lstlisting}
  herr_t H5VLreset_lib_state(void);
\end{lstlisting}
\end{mdframed}
Resets the internal state of the HDF5 library, undoing the
affects of H5VLrestore\_lib\_state.
This routine must be called as a "pair" with
{\tt H5VLrestore\_lib\_state}.  It can be called before, after, or
independently of {\tt H5VLfree\_lib\_state}.
Returns a positive value on success and a negative value on errors.
\bigskip

>>>>

\section{New VOL API Routines}
\label{sec:api}
API routines have been added to the HDF5 library to manage VOL connectors. This section details each new API call and explains its intended usage. Additionally, a set of API calls that map directly to the VOL callbacks themselves have been added to aid in the development of passthrough connectors which can be stacked and/or split. A list of these API calls is given in an appendix.

@@

\subsubsection{H5VLquery\_optional}
\begin{mdframed}[style=bgbox]
\textbf{Signature:}
\begin{lstlisting}
herr_t H5VLquery_optional(hid_t obj_id, H5VL_subclass_t subcls, int opt_type, uint64_t *flags);
\end{lstlisting}
\textbf{Arguments:}\\
\begin{tabular}{l p{13.5cm}}
  {\tt obj\_id} & (IN): A valid identifier of a VOL-managed object.\\
  {\tt subcls} & (IN): The subclass of the optional operation.\\
  {\tt opt\_type} & (IN): The optional operation. The native VOL connector uses hard-coded values. Other VOL connectors get this value when the optional operations are registered.\\
  {\tt flags} & (OUT): Bitwise flags indicating support and behavior.\\
\end{tabular}
\end{mdframed}
Determines if a connector or connector stack (determined from the passed-in object) supports an optional operation. The returned flags (listed below) not only indicate whether the operation is supported or not, but also give a sense of the option's behavior (useful for pass-through connectors).

Bitwise query flag values:
\begin{lstlisting}
#define H5VL_OPT_QUERY_SUPPORTED       0x0001 /* VOL connector supports this operation */
#define H5VL_OPT_QUERY_READ_DATA       0x0002 /* Operation reads data for object */
#define H5VL_OPT_QUERY_WRITE_DATA      0x0004 /* Operation writes data for object */
#define H5VL_OPT_QUERY_QUERY_METADATA  0x0008 /* Operation reads metadata for object */
#define H5VL_OPT_QUERY_MODIFY_METADATA 0x0010 /* Operation modifies metadata for object */
#define H5VL_OPT_QUERY_COLLECTIVE                                                                            \
    0x0020 /* Operation is collective (operations without this flag are assumed to be independent) */
#define H5VL_OPT_QUERY_NO_ASYNC  0x0040 /* Operation may NOT be executed asynchronously */
#define H5VL_OPT_QUERY_MULTI_OBJ 0x0080 /* Operation involves multiple objects */

\end{lstlisting}
\bigskip

@@

API calls to manage optional operations are also found in this header file.
These are discussed in the section on optional operations, above.

@@

\subsubsection{H5VLpeek\_connector\_id\_by\_name}
\begin{mdframed}[style=bgbox]
\textbf{Signature:}
\begin{lstlisting}
  hid_t H5VLpeek_connector_id_by_name(const char *name); 
\end{lstlisting}
\textbf{Arguments:}\\
\begin{tabular}{l p{13.5cm}}
 {\tt name} & (IN): name of the connector to query.\\
\end{tabular}
\end{mdframed}
Retrieves the ID for a registered VOL connector based on a connector name.
This is done without duplicating
the ID and transferring ownership to the caller (as it normally the case in the
HDF5 library). The ID returned from this operation should not be closed.
This is intended for use by VOL connectors to find their own ID.
Returns a negative value ({\tt H5I\_INVALID\_HID}) on errors.
\bigskip

\subsubsection{H5VLpeek\_connector\_id\_by\_value}
\begin{mdframed}[style=bgbox]
\textbf{Signature:}
\begin{lstlisting}
  hid_t H5VLpeek_connector_id_by_value(H5VL_class_value_t value); 
\end{lstlisting}
\textbf{Arguments:}\\
\begin{tabular}{l p{13.5cm}}
 {\tt value} & (IN): value of the connector to query.\\
\end{tabular}
\end{mdframed}
Retrieves the ID for a registered VOL connector based on a connector value.
This is done without duplicating
the ID and transferring ownership to the caller (as it normally the case in the
HDF5 library). The ID returned from this operation should not be closed.
This is intended for use by VOL connectors to find their own ID.
Returns a negative value ({\tt H5I\_INVALID\_HID}) on errors.
\bigskip

@@

\subsubsection{H5VLstart\_lib\_state}
\begin{mdframed}[style=bgbox]
\textbf{Signature:}
\begin{lstlisting}
  herr_t H5VLstart_lib_state(void);
\end{lstlisting}
\end{mdframed}
Opens a new internal state for the HDF5 library.
Returns a positive value on success and a negative value on errors.
\bigskip

@@

\subsubsection{H5VLfinish\_lib\_state}
\begin{mdframed}[style=bgbox]
\textbf{Signature:}
\begin{lstlisting}
  herr_t H5VLfinish_lib_state(void);
\end{lstlisting}
\end{mdframed}
Closes the state of the library, undoing the effects of {\tt H5VLstart\_lib\_state}.
Returns a positive value on success and a negative value on errors.
\bigskip
